An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2020-04-06 submission1/positive_results_SRs_RRs_submission.Rmd
Changed preprint to submission-ready manuscript for NHB: Shortened the abstract & removed Discussion subheadings, switched to "manuscript" mode, added line numbers, and tweaked the plots and tables to work in manuscript mode

abstract: > 
 When studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the evidence for scientific claims. Psychological scientists have been concerned about the degree of distortion in their literature due to publication bias and inflated Type-1 error rates. Registered Reports were developed with the goal to minimise such biases: In this new publication format, peer review and the decision to publish take place before the study results are known. We compared the results in the full population of published Registered Reports in Psychology ($N = 71$ as of November 2018) with a random sample of hypothesis-testing studies from the standard literature ($N = 152$) by searching 633 journals for the phrase ‘test* the hypothes*’ [replicating a method by @Fanelli2010]. Analysing the first hypothesis reported in each paper, we found $96\%$ positive results in standard reports, but only $44\%$ positive results in Registered Reports. The difference remained nearly as large when direct replications were excluded from the analysis ($96\%$ vs $50\%$ positive results). This large gap suggests that psychologists under-report negative results to an extent that threatens cumulative science. Although our study did not directly test the effectiveness of Registered Reports at reducing bias, these results show that the introduction of Registered Reports has led to a much larger proportion of negative results appearing in the published literature compared to standard reports.

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "en-UK"
class             : "jou"
output            : papaja::apa6_pdf
---

@@

```{r sampling, echo=FALSE, warning=FALSE, fig.cap = "(ref:sampling)", out.width = "\\textwidth", fig.env="figure*"}

@@

```{r mainplot, echo=FALSE, warning=FALSE, fig.height=5, fig.cap="(ref:mainplot)"}
#mainplot

#####
# Important alternative code and settings when using journal mode:
# 1. set fig.height=5 in chunk options (it's 4 in manuscript mode)
# 2. use the plot code below instead of `mainplot`
#    (otherwise font will be too small)!
#
ggplot(mainplot.df, aes(x = is_RR, y = value, fill = support)) +
                    geom_bar(stat = "identity",
                             width = 0.5) +
                    scale_fill_manual(values= c("#bcbddc", "#756bb1"),
                                      name="first hypothesis") +
                    annotate("text", label = paste("N =", n.SR),
                             x = 1, y = 105, size = 5) +
                    annotate("text", label = paste("N =", n.RR),
                             x = 2, y = 105, size = 5) +
                    geom_errorbar(aes(ymin = lower, ymax = upper),
                                  width = 0.05, size = 0.5) +
                    scale_x_discrete(breaks = waiver(),
                                     labels = c("SR" = "Standard\nReports",
                                                "RR" = "Registered\nReports"),
                                     name = NULL)+
                    scale_y_continuous(lim=c(0,110), breaks = c(seq(0, 100, 10)),
                                       minor_breaks = c(seq(0, 100, 5)),
                                       name = "% of papers", expand = c(0, 0))+
                    theme_minimal(base_size = 20)+
                    theme(panel.grid.major.x = element_blank(),
                          panel.grid.minor.x = element_blank(),
                          legend.margin = margin(0,0,0,-5.5)) +
                    coord_fixed(ratio=0.03)
```

@@

```{r echo = FALSE, results = 'asis'}
apa_table(
  phrasetable.orig
  , digits = c(0, 0, 0, 0, 0)
  , col.names = c("core word(s)", "introduction phrase", "abstract", 
                  "full text", "total")
  , align = c("l", "l", rep("r", 3))
  , caption = "(ref:table2)"
  , note = "Table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(3, 5))
  , midrules = c(10, 16, 22, 23, 28, 32)
  , landscape = FALSE
  , font_size = "footnotesize"
  , escape = TRUE
)
```

@@

```{r echo = FALSE, results = 'asis'}
# Important alternative settings when using journal mode: font_size = "footnotesize"
# (it's scriptsize in manuscript mode)
apa_table(
  phrasetable.rep
  , digits = c(0, 0, 0, 0, 0, 0, 0)
  , col.names = c("", "core word(s)", "introduction phrase", "abstract", 
                  "full text", "total", "")
  , align = c("l", "l", "l", rep("r", 4))
  , caption = "(ref:table3)"
  , note = "Table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no identifiable hypothesis introduction. Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(4, 6))
  , midrules = c(6, 10, 11, 12, 29, 30, 34, 35, 36)
  , landscape = FALSE
  , font_size = "footnotesize"
  , escape = TRUE
)
```

@@

```{r powerbaserate, echo=FALSE, fig.width=5, fig.height=3, fig.align='center', warning=FALSE, fig.cap="(ref:powerbaserate)", out.width = "0.6\\textwidth", fig.env="figure*"}

# Important altrnative chunk options when using journal mode: 
# 1. use out.width="0.6\\textwidth" (it's 0.8 in manuscript mode)
# 2. set fig.env="figure*"

@@

## Limitations
We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports. 
Because hypotheses, authors, and editors were not randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses. 
Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment. 
As mentioned above, it is *a-priori* plausible that the Registered Reports format is used selectively for particularly risky hypotheses. 
This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in Psychology. 
It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias. 
Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use. 
This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.

@@

## Conclusion
Our study presents a systematic comparison of positive results in Registered Reports and the standard literature. The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the existing body of published research. Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered Reports literature. The absence of negative results is a serious threat to a cumulative science. In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left. In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature---and may be one solution to achieve a more credible scientific record.

>>>>

abstract: > 
 Selectively publishing results that support the tested hypotheses ('positive' results) distorts the available evidence for scientific claims. For the past decade, psychological scientists have been increasingly concerned about the degree of such distortion in their literature. A new publication format has been developed to prevent selective reporting: In Registered Reports, peer review and the decision to publish take place before results are known. We compared the results in published Registered Reports (N = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (N = 152) in Psychology. Analysing the first hypothesis of each paper, we found $96\%$ positive results in standard reports, but only $44\%$ positive results in Registered Reports. We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "en-UK"
class             : "man"
output            : papaja::apa6_pdf
---

@@

```{r sampling, echo=FALSE, warning=FALSE, fig.cap = "(ref:sampling)", out.width = "\\textwidth"}

@@

```{r mainplot, echo=FALSE, warning=FALSE, fig.height=4, fig.cap="(ref:mainplot)"}
mainplot

#####
# Important alternative code and settings when using journal mode:
# 1. set fig.height=5 in chunk options (it's 4 in manuscript mode)
# 2. use the plot code below instead of `mainplot`
#    (otherwise font will be too small)!
#

#ggplot(mainplot.df, aes(x = is_RR, y = value, fill = support)) +
#                    geom_bar(stat = "identity",
#                             width = 0.5) +
#                    scale_fill_manual(values= c("#bcbddc", "#756bb1"),
#                                      name="first hypothesis") +
#                    annotate("text", label = paste("N =", n.SR),
#                             x = 1, y = 105, size = 5) +
#                    annotate("text", label = paste("N =", n.RR),
#                             x = 2, y = 105, size = 5) +
#                    geom_errorbar(aes(ymin = lower, ymax = upper),
#                                  width = 0.05, size = 0.5) +
#                    scale_x_discrete(breaks = waiver(),
#                                     labels = c("SR" = "Standard\nReports",
#                                                "RR" = "Registered\nReports"),
#                                     name = NULL)+
#                    scale_y_continuous(lim=c(0,110), breaks = c(seq(0, 100, 10)),
#                                       minor_breaks = c(seq(0, 100, 5)),
#                                       name = "% of papers", expand = c(0, 0))+
#                    theme_minimal(base_size = 20)+
#                    theme(panel.grid.major.x = element_blank(),
#                          panel.grid.minor.x = element_blank(),
#                          legend.margin = margin(0,0,0,-5.5)) +
#                    coord_fixed(ratio=0.03)
```

@@

```{r echo = FALSE, results = 'asis'}
apa_table(
  phrasetable.orig
  , digits = c(0, 0, 0, 0, 0)
  , col.names = c("core word(s)", "introduction phrase", "abstract", 
                  "full text", "total")
  , align = c("l", "l", rep("r", 3))
  , caption = "(ref:table2)"
  , note = "Table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(3, 5))
  , midrules = c(10, 16, 22, 23, 28, 32)
  , landscape = FALSE
  , font_size = "scriptsize"
  , escape = TRUE
)
```

@@

```{r echo = FALSE, results = 'asis'}
# Important alternative settings when using journal mode: font_size = "footnotesize"
# (it's scriptsize in manuscript mode)
apa_table(
  phrasetable.rep
  , digits = c(0, 0, 0, 0, 0, 0, 0)
  , col.names = c("", "core word(s)", "introduction phrase", "abstract", 
                  "full text", "total", "")
  , align = c("l", "l", "l", rep("r", 4))
  , caption = "(ref:table3)"
  , note = "Table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no identifiable hypothesis introduction. Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(4, 6))
  , midrules = c(6, 10, 11, 12, 29, 30, 34, 35, 36)
  , landscape = FALSE
  , font_size = "scriptsize"
  , escape = TRUE
)
```

@@

```{r powerbaserate, echo=FALSE, fig.width=5, fig.height=3, fig.align='center', warning=FALSE, fig.cap="(ref:powerbaserate)", out.width = "0.8\\textwidth"}

# Important alternative chunk options when using journal mode: 
# 1. use out.width="0.6\\textwidth" (it's 0.8 in manuscript mode)
# 2. set fig.env="figure*"

@@

We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports. 
Because hypotheses, authors, and editors were not randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses. 
Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment. 
As mentioned above, it is *a-priori* plausible that the Registered Reports format is used selectively for particularly risky hypotheses. 
This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in Psychology. 
It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias. 
Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use. 
This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.

@@

Our study presents a systematic comparison of positive results in Registered Reports and the standard literature. The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the existing body of published research. Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered Reports literature. The absence of negative results is a serious threat to a cumulative science. In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left. In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature---and may be one solution to achieve a more credible scientific record.

### 2020-04-06 submission1/positive_results_SRs_RRs_submission.tex
Changed preprint to submission-ready manuscript for NHB: Shortened the abstract & removed Discussion subheadings, switched to "manuscript" mode, added line numbers, and tweaked the plots and tables to work in manuscript mode

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[british,,jou,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={An excess of positive results: Comparing the standard Psychology literature with Registered Reports},
            pdfkeywords={Publication bias, Registered Reports, hypothesis testing},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

Correspondence concerning this article should be addressed to Anne M. Scheel, Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands. E-mail: a.m.scheel@tue.nl}
\keywords{Publication bias, Registered Reports, hypothesis testing}
\usepackage{dblfloatfix}

\usepackage{float}
\usepackage{framed}
\usepackage{caption}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1, small}, skip=10pt}
\captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
\newfloat{textbox}{thp}{lop}
\floatname{textbox}{Box}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=british]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[variant=british]{english}
\fi

@@

\abstract{
When studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the evidence for scientific claims. Psychological scientists have been concerned about the degree of distortion in their literature due to publication bias and inflated Type-1 error rates. Registered Reports were developed with the goal to minimise such biases: In this new publication format, peer review and the decision to publish take place before the study results are known. We compared the results in the full population of published Registered Reports in Psychology (\(N = 71\) as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (\(N = 152\)) by searching 633 journals for the phrase `test* the hypothes*' (replicating a method by Fanelli, 2010). Analysing the first hypothesis reported in each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports. The difference remained nearly as large when direct replications were excluded from the analysis (\(96\%\) vs \(50\%\) positive results). This large gap suggests that psychologists under-report negative results to an extent that threatens cumulative science. Although our study did not directly test the effectiveness of Registered Reports at reducing bias, these results show that the introduction of Registered Reports has led to a much larger proportion of negative results appearing in the published literature compared to standard reports.
}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{sampling_process_flowchart} \caption{Sampling process and exclusions for standard reports and Registered Reports. Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had been excluded erroneously. \enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance (we chose to exclude these cases to be conservative).}\label{fig:sampling}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics{positive_results_SRs_RRs_files/figure-latex/mainplot-1.pdf}
\caption{\label{fig:mainplot}Positive result rates for standard reports and Registered Reports. Error bars indicate \(95 \%\) confidence intervals around the observed positive result rate.}
\end{figure}

@@

\footnotesize{

@@

\begin{figure*}

{\centering \includegraphics[width=0.6\textwidth]{positive_results_SRs_RRs_files/figure-latex/powerbaserate-1}

@@

\caption{Combinations of the proportion of true hypotheses and statistical power that would produce the observed positive result rates given \(\alpha = 5 \%\) and no bias. Shaded areas indicate \(95\%\) confidence intervals. SRs = standard reports, RRs = Registered Reports. The curve for all SRs (i.e, including replications; \(96.05 \%\) positive results, \(N = 152\)) is not shown because it is almost identical to the one for original SRs. Plotted values were calculated using the equation \(PRR = \alpha*(1-t) + (1-\beta)*t\); with \(PRR =\) positive result rate, \(\alpha =\) probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), \(1-\beta =\) probability of obtaining a positive result when testing a true hypothesis (power), and \(t =\) proportion of true hypotheses; and solving for \(t\) and \(1-\beta\), respectively (with the simplifying assumption that all studies in one group have the same power).}\label{fig:powerbaserate}
\end{figure*}

@@

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

@@

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

>>>>

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[british,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={An excess of positive results: Comparing the standard Psychology literature with Registered Reports},
            pdfkeywords={Publication bias, Registered Reports, hypothesis testing},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

Correspondence concerning this article should be addressed to Anne M. Scheel, Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands. E-mail: a.m.scheel@tue.nl}
\keywords{Publication bias, Registered Reports, hypothesis testing}
\usepackage{lineno}

\linenumbers
\usepackage{float}
\usepackage{framed}
\usepackage{caption}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1, small}, skip=10pt}
\captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
\newfloat{textbox}{thp}{lop}
\floatname{textbox}{Box}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=british]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[variant=british]{english}
\fi

@@

\abstract{
Selectively publishing results that support the tested hypotheses (`positive' results) distorts the available evidence for scientific claims. For the past decade, psychological scientists have been increasingly concerned about the degree of such distortion in their literature. A new publication format has been developed to prevent selective reporting: In Registered Reports, peer review and the decision to publish take place before results are known. We compared the results in published Registered Reports (N = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (N = 152) in Psychology. Analysing the first hypothesis of each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports. We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
}

@@

\begin{figure}
\includegraphics[width=\textwidth]{sampling_process_flowchart} \caption{Sampling process and exclusions for standard reports and Registered Reports. Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had been excluded erroneously. \enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance (we chose to exclude these cases to be conservative).}\label{fig:sampling}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{positive_results_SRs_RRs_submission_files/figure-latex/mainplot-1.pdf}
\caption{\label{fig:mainplot}Positive result rates for standard reports and Registered Reports. Error bars indicate \(95 \%\) confidence intervals around the observed positive result rate.}
\end{figure}

@@

\scriptsize{

@@

\begin{figure}

{\centering \includegraphics[width=0.8\textwidth]{positive_results_SRs_RRs_submission_files/figure-latex/powerbaserate-1}

@@

\caption{Combinations of the proportion of true hypotheses and statistical power that would produce the observed positive result rates given \(\alpha = 5 \%\) and no bias. Shaded areas indicate \(95\%\) confidence intervals. SRs = standard reports, RRs = Registered Reports. The curve for all SRs (i.e, including replications; \(96.05 \%\) positive results, \(N = 152\)) is not shown because it is almost identical to the one for original SRs. Plotted values were calculated using the equation \(PRR = \alpha*(1-t) + (1-\beta)*t\); with \(PRR =\) positive result rate, \(\alpha =\) probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), \(1-\beta =\) probability of obtaining a positive result when testing a true hypothesis (power), and \(t =\) proportion of true hypotheses; and solving for \(t\) and \(1-\beta\), respectively (with the simplifying assumption that all studies in one group have the same power).}\label{fig:powerbaserate}
\end{figure}

@@

@@
